Instructions for developing new pages for the MarineOmics webpage

### 2023-12-14 DRAFT_DNA_methylation.Rmd
more meth tutorial edits (align)

---
title: 'DNA Methylation Analyses'
subtitle: '*Steven Roberts*, *Sam White*, and *Yaamini Venkataraman*'
bibliography: DRAFT_DNA_methylation/DNA-Methylation.bib
---

@@

*Frequency distribution of methylation ratios for CpG dinucleotides in oyster gill tissue.* DOI: [10.7717/peerj.215/fig-1](https://doi.org/10.7717/peerj.215/fig-1)

@@

@@

This will result in a prepared genome with associated new directories including

@@

This will create bam files (sequence alignment files)

@@

This particular command is used to extract and process methylation data from BAM files (generated after sequencing data alignment). Let's break down the command and its options:

1.  **Command Base**:

    -   **`${bismark_dir}/bismark_methylation_extractor`**: This specifies the path to the **`bismark_methylation_extractor`** executable within the Bismark software directory. The variable **`${bismark_dir}`** holds the path to the Bismark installation directory.

2.  **Options**:

>>>>

---
title: 'DNA Methylation Analyses'
subtitle: '*Yaamini Venkataraman*, *Sam White*, and *Steven Roberts*'
bibliography: DRAFT_DNA_methylation/DNA-Methylation.bib
---

@@

@@

## Considerations

@@

Bismark will create the following subdirectories as outputs of the above code for genome preparation

@@

This will create BAM files (sequence alignment files)

@@

This particular command is used to extract and process methylation data from BAM files (generated after sequencing data alignment). Let's break down the options:

1.  **Options**:
